Impact of grids and dynamical cores in CESM2.2 on the meteorology and climate of the Arctic

### 2021-03-11 arcticgrids.tex
new figures

\begin{figure}[t]
\begin{center}
         \includegraphics[width=60mm]{figs/temp_grisres.pdf}
\end{center}
\caption{.}
\label{fig:prect}
\end{figure}

@@

@@

\begin{figure}[t]
\begin{center}
         \includegraphics[width=100mm]{figs/temp_tseries_GRIS.pdf}
\end{center}
\caption{.}
\label{fig:tseries}
\end{figure}

>>>>

\begin{figure}[t]
\begin{center}
\begin{tabular}{cccc}
         \includegraphics[width=60mm]{figs/temp_grisres_dxoverglc.pdf}&
         \includegraphics[width=60mm]{figs/temp_grisres_error.pdf} \\
\end{tabular}
\end{center}
\caption{.}
\label{fig:prect}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
         \includegraphics[width=100mm]{figs/temp_tseries_GRIS_map_TO_f19.pdf}
\end{center}
\caption{.}
\label{fig:tseries}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\begin{tabular}{cccc}
         \includegraphics[width=100mm]{figs/temp_ktransect.pdf} \\
         \includegraphics[width=100mm]{figs/temp_btransect.pdf} \\
\end{tabular}
\end{center}
\caption{.}
\label{fig:prect}
\end{figure}

\begin{figure}[t]
\begin{center}
\begin{tabular}{cccc}
         \includegraphics[width=60mm]{figs/temp_zsmb_btrans_obsperiod.pdf}&
         \includegraphics[width=60mm]{figs/temp_zsmb_ktrans_obsperiod.pdf} \\
\end{tabular}
\end{center}
\caption{.}
\label{fig:prect}
\end{figure}
